Supporting information: Copulas and their potential for ecology

### 2019-10-01 Paper.Rmd
Tables fixed, autolink added

```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
options(scipen = 1, digits = 5) #This option round all numbers appeared in the inline r code upto 5th digit
#seed<-101
#source("mtime.R") #A function needed for caching
```

@@

```{r read_RES_aphid_count, echo=F}
RES_aphid_count<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_count_species_10.RDS")
```

@@

<!--bivariate example, model selection-->
For the soil C and N data (Data section, Table \ref{tab_data_info}, 
Fig. \ref{fig_biv_multi_raw_cop}A), variables were 
non-independent ($p=$ `r BivMS_res_Loecke$IndepTestRes`, to within the precision available 
from `BiCopIndTest` in the `VineCopula` package); non-independence is also visually apparent.
The Kendall correlation was `r round(BivMS_res_Loecke$TauVal,2)`. We fitted our 16 copulas
to the normalized ranks (Fig. \ref{fig_biv_multi_raw_cop}E) 
and computed AIC and BIC weights and corresponding
lower- and upper-tail statistics for the fitted distributions (Table \ref{tab_soilCNfit}).
`r BivMS_res_Loecke$InfCritRes$copname[which.max(BivMS_res_Loecke$InfCritRes$AICw)]` was the 
minimum-AIC copula, with AIC `r round(min(BivMS_res_Loecke$InfCritRes$AIC),2)`, whereas the 
normal copula had a much higher AIC, $-6333.16$, 
<!--***DAN: Shyamolina, please make this an autolink. Please make 
sure to round to two digits after the decimal, as with the AIC best value
presented just above.-->
answering the 
first part of Q1 for these data. Recall that AIC differences of $2$
or $3$ are considered meaningful and differences of $8$ or greater
are considered diffinitive, so that data provide essentially no support
for the higher-AIC model in that case [@burnham2003_modelselection].
Model-averaged lower- and upper-tail dependence statistics were `r round(BivMS_res_Loecke$relLTdep_AICw,3)` 
and `r round(BivMS_res_Loecke$relUTdep_AICw,3)`, respectively (AIC weights were used for averaging). 
These values are distinct from what a normal copula would give, namely, 0, helping to answer 
the second part 
Q1 for these data. The values also differed substantially 
from each other, helping answer the third part of Q1. 
The numbers reflect stronger upper- than lower-tail
dependence, and this is also visible in the extreme upper-right
and lower-left corners of the copula plot (Fig. \ref{fig_biv_multi_raw_cop}E).

@@

We present green spruce aphid abundance (Data section; Table \ref{tab_data_info}) results
as an example multivariate analysis.
Independence was rejected for each pair of the 10 sampling locations. 
Best-fitting (lowest-AIC) copulas were non-normal
for the large majority of location pairs (72 of 90 pairs), 
<!--***DAN: Shyamolina, please make these numbers autolinks-->
and the AIC
of the normal copula minus the minimum AIC, averaged across 
location pairs, was $2.732$.
<!--***DAN: Shyamolina, please make this an autolink, so the value is
automatically filled in even if it changes-->
Whereas $2.732$
<!--***DAN: Shyamolna, again, autolink, please-->
would be only a marginally meaningful AIC difference for a single
location pair, it is more meaningful as an average across many
pairs. Relatedly, and illustrating the concept here, 
the chances of getting 72 or more 
non-normal location pairs if the chances were equal of getting
a normal versus a non-normal result (and taking into account that
the location pair (A,B) will necessarily 
produce the same result as the pair
(B,A)) is low, $`r 1-pbinom(72/2-1,45,.5)`$. 
<!--***DAN: Shyamolina, please replace the 72 in the above expression
by an autolink, and make this show
3 significant digits, i.e., it should show 3.29e-5, not 3.287332e-05-->
These results help answer the first part of Q1: non-normal
copula structure appears to be meaningfully common in
these data, even if not universal.
Goodness of fit tests in every case 
failed to reject the hypothesis that the AIC-best copula 
family was also 
an objectively adequate description of 
the data; i.e., the collection of 
copula families we used was sufficiently broad to characterize 
these data. Model-averaged lower- and upper-tail
dependence statistics had $2.5$th and $97.5$th quantiles
$(0.123,0.721)$ and $(0.002,0.41)$, respectively,
<!--***DAN: Shyamolina, autolinks pls -->
thereby commonly differing 
from what a normal copula would give (i.e., 0), and helping to
answer the second
part of Q1: these data have greater tail dependence 
(lower and upper) than would be expected from a normal-copula null hypothesis. We note however that our model selection 
procedures again do not reveal whether tail-dependence 
parameters are *significantly* different from $0$, and we refer 
the reader to nonparametric results below for information
on significance. 
Model-averaged lower- minus upper-tail dependence statistics 
were positive for all but a few location pairs (`r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)` 
out of `r (dim(RES_aphid_count$gfc_p_CvM)[1]^2-dim(RES_aphid_count$gfc_p_CvM)[1])-2*RES_aphid_count$num_indep_loc_pair`). The chances
of getting `r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)` 
or more positive values, here, under a null hypothesis of equal chances 
for positive and negative values (and again accounting for the fact that location pairs (A,B) and (B,A) will show the same result) was
again low, $`r 1-pbinom(86/2-1,45,.5)`$. 
<!--***DAN: Shyamolina, please autolink this, and use 3 sig figs as 
before-->
Thus the spatial synchrony of rarity in the green spruce aphid is stronger 
than the spatial synchrony of outbreaks. This answers the third part of Q1.

@@

<!--***DAN: Shyamolina, can you please insert code to make what
is currently Table S7 appear here? Please also make it disappear from
the sup mat. I want to move it from there to here, please. I am
talking about the table with label tab_count_resamp. Please also
search both the main text and the supp mat for that label, and 
fix references - you may have to fix some prefixes (SM-, MT-), since
the table will have moved from sup mat to main text.-->

@@

Asymmetry results were generally verified by nonparametric approaches,
with the exception of the methane-flux data. 
For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\cor_l-\cor_u$ were 
(`r unname(round(stat_aphid_ff$numericdf[10,c(3,4)],3))`)
for the leaf-curling plum aphid first flight data
(Table \ref{tab_multivar_summary}, row 9), 
indicating greater upper-tail dependence, and consistent with
the results of Table \ref{MT-tab_multivar_summary}, row 8. 
For the *Ceratium furca* abundance data, confidence intervals were
(`r unname(round(stat_plankton_north_sea$numericdf[10,c(3,4)],3))`), 
indicating greater lower-tail dependence, and again 
consistent with the results of Table \ref{MT-tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
(`r unname(round(stat_methane$numericdf[10,c(3,4)],3))`);
the asymmetry in tail dependence revealed by the model selection
results for the methane-flux data was apparently not strong enough to
also be revealed by the nonparametric analyses. 
Analogues to Table \ref{tab_count_resamp} are in Tables
\ref{SM-tab_ff_resamp}-\ref{SM-tab_methane_resamp}.
Our generally
affirmative, empirically based answer to Q1 for the multivariate datasets is 
represented in Fig. \ref{MasterFigure} as solid outlines around the names
of those datasets, in the middle row of boxes.
We also carried out the same analyses for abundance and first-flight data for the 18 
aphid species for which we had data other than the green spruce and leaf-curling plum aphids,
as well as for the 21 plankton taxa for which we had abundance data other than
\textit{Ceratium furca} (results not shown); results supported the conclusion that 
non-normal copula structure and tail dependence, and asymmetry of tail dependence are 
common.

@@

<!--summary table : results with multi-variate data-->
```{r tab_multivar_summaryl, echo=F, results='asis',message=F}
tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
tab1<-tab_multivar_summary[c(1:7,9,11,12,14,16),] # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change
tab2<-tab_multivar_summary[c(8,10,13,15,17),]  # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change

two_tab_in1 <- as.data.frame(do.call(cbind, lapply(1:ncol(tab1), function(i) paste0(" (",tab1[c(7:8,10:12),i], ", ",tab2[ , i], ")") )))   # see carefully if you rearrange tab_multivar_summary's row in suppmat this will change

colnames(two_tab_in1)<-colnames(tab_multivar_summary)
rownames(two_tab_in1)<-c("CI_LT","CI_UT","CI_Pl","CI_Pu","CI_Pl-Pu")

tab_multivar_summary<-rbind(tab_multivar_summary[c(1:3,5,6),],
                            two_tab_in1[1:2,], #CI of LT, CI of UT
                            tab_multivar_summary[11,],
                            two_tab_in1[5,] #CI of Pl-Pu
                           )

row.names(tab_multivar_summary)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-normal copula as best fit",
           #"4. Avg. of normal-AICw minus bestfit-copula AICw across location pairs",
           "4. Average of AIC differences (normal AIC minus min AIC) across location pairs",
           "5. Number of well-fitting location pairs",
           "6. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. lower-tail dependence",
           "7. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. upper-tail dependence",
           "8. Percent pairs showing stronger lower tail dependence",
           "9. 2.5$^{th}$ and 97.5$^{th}$ quantiles of $<$P$_{l}$ - P${_u}$$>$ across all location pair")
           )

tab_multivar_summary<-cbind(dt,tab_multivar_summary)

knitr::kable(tab_multivar_summary[1:8,], 
             format="latex", escape = F,
             caption.short = "Summary of results for multivariate datasets",
             caption = "Summary of Q1 results for multivariate datasets. Rows 3-8 of the table were computed for the non-independent pairs (row 2) only. A well-fitting location pair (row 5) was one for which the best-fitting copula had $p$-values $>0.01$ for both the Cramer-von Mises and Kolmogorov-Smirnov goodness of fit tests. \\label{tab_multivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ","Green spruce aphid abundance",
                        "Leaf-curling plum aphid first flight",
                        "\\textit{Ceratium furca} abundance","Methane-flux")
             )%>%column_spec(2:5,width="2.4cm")%>%
             column_spec(1, width = "6cm")%>%kable_styling(latex_options = "basic",position = "center")
```

>>>>

```{r setup_Paper, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
options(scipen = 1, digits = 2) #This option round all numbers appeared in the inline r code upto specified digit
#seed<-101
#source("mtime.R") #A function needed for caching
```

@@

```{r read_RES_aphid_count, echo=F}
RES_aphid_count<-readRDS("./Results/fitting_results/AphidCopulaFit_selecloc_count_species_10.RDS")
#------------ also reading some extra stuffs -------
stat_aphid_count<-readRDS("./Results/stat_results/stat_aphid_count/stat_aphid_count_sp_10.RDS")
stat_aphid_ff<-readRDS("./Results/stat_results/stat_aphid_ff/stat_aphid_ff_sp_11.RDS")
stat_plankton_north_sea<-readRDS("./Results/stat_results/stat_plankton_north_sea/stat_plankton_north_sea_sp_16.RDS")
stat_methane<-readRDS("./Results/stat_results/stat_methane/stat_methane.RDS")
tab_multivar_summary<-readRDS("./Results/tab_multivar_summary.RDS")
```

@@

<!--bivariate example, model selection-->
For the soil C and N data (Data section, Table \ref{tab_data_info}, 
Fig. \ref{fig_biv_multi_raw_cop}A), variables were 
non-independent ($p=$ `r BivMS_res_Loecke$IndepTestRes`, to within the precision available 
from `BiCopIndTest` in the `VineCopula` package); non-independence is also visually apparent.
The Kendall correlation was `r round(BivMS_res_Loecke$TauVal,2)`. We fitted our 16 copulas
to the normalized ranks (Fig. \ref{fig_biv_multi_raw_cop}E) 
and computed AIC and BIC weights and corresponding
lower- and upper-tail statistics for the fitted distributions (Table \ref{tab_soilCNfit}).
`r BivMS_res_Loecke$InfCritRes$copname[which.min(BivMS_res_Loecke$InfCritRes$AIC)]` was the 
minimum-AIC copula, with AIC `r round(min(BivMS_res_Loecke$InfCritRes$AIC),2)`, whereas the 
normal copula had a much higher AIC, `r round(BivMS_res_Loecke$InfCritRes$AIC[1],2)`, answering the 
first part of Q1 for these data. Recall that AIC differences of $2$
or $3$ are considered meaningful and differences of $8$ or greater
are considered diffinitive, so that data provide essentially no support
for the higher-AIC model in that case [@burnham2003_modelselection].
Model-averaged lower- and upper-tail dependence statistics were `r round(BivMS_res_Loecke$relLTdep_AICw,3)` 
and `r round(BivMS_res_Loecke$relUTdep_AICw,3)`, respectively (AIC weights were used for averaging). 
These values are distinct from what a normal copula would give, namely, 0, helping to answer 
the second part 
Q1 for these data. The values also differed substantially 
from each other, helping answer the third part of Q1. 
The numbers reflect stronger upper- than lower-tail
dependence, and this is also visible in the extreme upper-right
and lower-left corners of the copula plot (Fig. \ref{fig_biv_multi_raw_cop}E).

@@

We present green spruce aphid abundance (Data section; Table \ref{tab_data_info}) results
as an example multivariate analysis.
Independence was rejected for each pair of the 10 sampling locations. 
Best-fitting (lowest-AIC) copulas were non-normal
for the large majority of location pairs (`r tab_multivar_summary$Green_spruce_aphid_count$num.non_N` of `r tab_multivar_summary$Green_spruce_aphid_count$num.pairs` pairs), 
and the AIC
of the normal copula minus the minimum AIC, averaged across 
location pairs, was `r tab_multivar_summary$Green_spruce_aphid_count$Avg.N_minus_bestfit.AIC`.
Whereas `r tab_multivar_summary$Green_spruce_aphid_count$Avg.N_minus_bestfit.AIC`
would be only a marginally meaningful AIC difference for a single
location pair, it is more meaningful as an average across many
pairs. Relatedly, and illustrating the concept here, 
the chances of getting `r tab_multivar_summary$Green_spruce_aphid_count$num.non_N` or more 
non-normal location pairs if the chances were equal of getting
a normal versus a non-normal result (and taking into account that
the location pair (A,B) will necessarily 
produce the same result as the pair
(B,A)) is low, 
$`r 1-pbinom(tab_multivar_summary$Green_spruce_aphid_count$num.non_N/2-1,45,0.5)`$. 
These results help answer the first part of Q1: non-normal
copula structure appears to be meaningfully common in
these data, even if not universal.
Goodness of fit tests in every case 
failed to reject the hypothesis that the AIC-best copula 
family was also 
an objectively adequate description of 
the data; i.e., the collection of 
copula families we used was sufficiently broad to characterize 
these data. Model-averaged lower- and upper-tail
dependence statistics had $2.5^{th}$ and $97.5^{th}$ quantiles
(`r tab_multivar_summary$Green_spruce_aphid_count$LT_0.025_CI`, `r tab_multivar_summary$Green_spruce_aphid_count$LT_0.975_CI`) and 
(`r tab_multivar_summary$Green_spruce_aphid_count$UT_0.025_CI`, `r tab_multivar_summary$Green_spruce_aphid_count$UT_0.975_CI`), respectively,
thereby commonly differing 
from what a normal copula would give (i.e., 0), and helping to
answer the second
part of Q1: these data have greater tail dependence 
(lower and upper) than would be expected from a normal-copula null hypothesis. We note however that our model selection 
procedures again do not reveal whether tail-dependence 
parameters are *significantly* different from $0$, and we refer 
the reader to nonparametric results below for information
on significance. 
Model-averaged lower- minus upper-tail dependence statistics 
were positive for all but a few location pairs (`r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)` 
out of `r (dim(RES_aphid_count$gfc_p_CvM)[1]^2-dim(RES_aphid_count$gfc_p_CvM)[1])-2*RES_aphid_count$num_indep_loc_pair`). The chances
of getting `r sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)` 
or more positive values, here, under a null hypothesis of equal chances 
for positive and negative values (and again accounting for the fact that location pairs (A,B) and (B,A) will show the same result) was
again low, 
$`r 1-pbinom(sum((RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw)>0,na.rm=T)/2-1,45,0.5)`$.
Thus the spatial synchrony of rarity in the green spruce aphid is stronger 
than the spatial synchrony of outbreaks. This answers the third part of Q1.

@@

<!--***DAN: Shyamolina, can you please insert code to make what
is currently Table S7 appear here? Please also make it disappear from
the sup mat. I want to move it from there to here, please. I am
talking about the table with label tab_count_resamp. Please also
search both the main text and the supp mat for that label, and 
fix references - you may have to fix some prefixes (SM-, MT-), since
the table will have moved from sup mat to main text.-->
<!--Show the statistical results in a table for green spruce aphid abundance data-->

```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s, digits = 3,
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

Asymmetry results were generally verified by nonparametric approaches,
with the exception of the methane-flux data. 
For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\cor_l-\cor_u$ were 
(`r unname(round(stat_aphid_ff$numericdf[10,c(3,4)],3))`)
for the leaf-curling plum aphid first flight data
(Table \ref{tab_multivar_summary}, row 9), 
indicating greater upper-tail dependence, and consistent with
the results of Table \ref{tab_multivar_summary}, row 8. 
For the *Ceratium furca* abundance data, confidence intervals were
(`r unname(round(stat_plankton_north_sea$numericdf[10,c(3,4)],3))`), 
indicating greater lower-tail dependence, and again 
consistent with the results of Table \ref{tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
(`r unname(round(stat_methane$numericdf[10,c(3,4)],3))`);
the asymmetry in tail dependence revealed by the model selection
results for the methane-flux data was apparently not strong enough to
also be revealed by the nonparametric analyses. 
Analogues to Table \ref{tab_count_resamp} are in Tables
\ref{SM-tab_ff_resamp}-\ref{SM-tab_methane_resamp}.
Our generally
affirmative, empirically based answer to Q1 for the multivariate datasets is 
represented in Fig. \ref{MasterFigure} as solid outlines around the names
of those datasets, in the middle row of boxes.
We also carried out the same analyses for abundance and first-flight data for the 18 
aphid species for which we had data other than the green spruce and leaf-curling plum aphids,
as well as for the 21 plankton taxa for which we had abundance data other than
\textit{Ceratium furca} (results not shown); results supported the conclusion that 
non-normal copula structure and tail dependence, and asymmetry of tail dependence are 
common.

@@

<!--summary table : results with multi-variate data-->
```{r tab_multivar_summaryl, echo=F, results='asis',message=F}
tab_multivar_summaryl<-tab_multivar_summary[-c(4,12:15),] #exclude extra rows for AICw, Corl, Coru

tab1<-tab_multivar_summaryl[c(6,8,12),] # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change
tab2<-tab_multivar_summaryl[c(7,9,13),]  # see carefully if you rearrange tab_multivar_summary's row
                                                   #in suppmat this will change

two_tab_in1 <- as.data.frame(do.call(cbind, lapply(1:ncol(tab1), function(i) paste0(" (",tab1[,i], ", ", tab2[ , i], ")") )))   # see carefully if you rearrange tab_multivar_summary's row in suppmat this will change

two_tab_in1_again <- as.data.frame(do.call(cbind, lapply(1:ncol(two_tab_in1), 
                                                         function(i) paste0(tab_multivar_summaryl[11,i], ", ", two_tab_in1[3,i]) )))

colnames(two_tab_in1)<-colnames(two_tab_in1_again)<-colnames(tab_multivar_summaryl)

compiled_tab<-rbind(two_tab_in1[1:2,],two_tab_in1_again)
rownames(compiled_tab)<-c("CI_LT","CI_UT","Avg_CI_Corl-Coru")

tab_multivar_summary_ed<-rbind(tab_multivar_summaryl[c(1:5),],
                            compiled_tab[1:2,], #CI of LT, CI of UT
                            tab_multivar_summaryl[10,],
                            compiled_tab[3,] #avg and CI of Corl-Coru
                           )

row.names(tab_multivar_summary_ed)<-NULL
library(kableExtra)
library(dplyr)
library(tibble)
dt <- tibble(
            Description = c("1. Location pairs (excluding self comparisons)",
           "2. Number of non-independent pairs",
           "3. Number of pairs with non-normal copula as best fit",
           "4. Average of AIC differences (normal AIC minus min AIC) across location pairs",
           "5. Number of well-fitting location pairs",
           "6. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. lower-tail dependence",
           "7. 2.5$^{th}$ and 97.5$^{th}$ quantiles of model-avg. upper-tail dependence",
           "8. Percent pairs showing stronger lower tail dependence",
           "9. Mean with 2.5$^{th}$ and 97.5$^{th}$ quantiles of Cor$_{l}$ - Cor${_u}$ across all location pair")
           )

tab_multivar_summary_ed<-cbind(dt,tab_multivar_summary_ed)

knitr::kable(tab_multivar_summary_ed, 
             format="latex", escape = F,
             caption.short = "Summary of results for multivariate datasets",
             caption = "Summary of Q1 results for multivariate datasets. Rows 3-8 of the table were computed for the non-independent pairs (row 2) only. A well-fitting location pair (row 5) was one for which the best-fitting copula had $p$-values $>0.01$ for both the Cramer-von Mises and Kolmogorov-Smirnov goodness of fit tests. \\label{tab_multivar_summary}",
             booktabs=T, linesep = "\\addlinespace",
             col.names = c(" ","Green spruce aphid abundance",
                        "Leaf-curling plum aphid first flight",
                        "\\textit{Ceratium furca} abundance","Methane-flux")
             )%>%column_spec(2:5,width="2.5cm")%>%
             column_spec(1, width = "6cm")%>%kable_styling(latex_options = "basic",position = "center")
```

### 2019-10-01 SupportingInformation.Rmd
Tables fixed, autolink added

<!--Show the statistical results in a table for green spruce aphid abundance data-->
```{r tab_count_resamp,echo=F,results="markup"}
s<-stat_aphid_count$numericdf[,c(3,2,4)]
sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s, digits = 3,
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             format = "latex",linesep = "", escape = F,align="c",
             caption.short="Results for nonparametric statistics, green spruce aphid abundance data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for green spruce aphid abundance data.\\label{tab_count_resamp}",
             booktabs=TRUE)
```

@@

  m<-matrix(NA,1,17)
  colnames(m)<-c("num.pairs","num.non-indep","num.non-N",
                 "Avg.N_minus_bestfit.AICw","Avg.N_minus_bestfit.AIC","num.good.fit",
                 "0.025-CI.LT","0.975-CI.LT","0.025-CI.UT","0.975-CI.UT",
                 "percent.LT-UT>0",
                 "0.025-CI.Pl","0.975-CI-Pl","0.025-CI.Pu","0.975-CI.Pu","0.025-CI.Pl-Pu","0.975-CI.Pl-Pu")
  m<-as.data.frame(m)

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$`num.non-indep`<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)

  bcop<-r$info_ord_copcode[,,1] # matrix with best fit copula name
  bcop[bcop==Inf]<-NaN # replacing Independent pairs with NaN
  m$`num.non-N`<-sum(bcop!=1,na.rm = T)

@@

  pcvm<-r$gfc_p_CvM
  pcvm[pcvm==Inf]<-NaN
  pks<-r$gfc_p_KS
  pks[pks==Inf]<-NaN
  temp<-which((pcvm>0.01) & (pks>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.LT`<-round(CI_LT[1],3)
  m$`0.975-CI.LT`<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.UT`<-round(CI_UT[1],3)
  m$`0.975-CI.UT`<-round(CI_UT[2],3)
  m$`percent.LT-UT>0`<-round((sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)/((d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)))*100,2)
  m$`0.025-CI.Pl`<-round(rs$numericdf[5,3],3)
  m$`0.975-CI-Pl`<-round(rs$numericdf[5,4],3)
  m$`0.025-CI.Pu`<-round(rs$numericdf[6,3],3)
  m$`0.975-CI.Pu`<-round(rs$numericdf[6,4],3)
  m$`0.025-CI.Pl-Pu`<-round(rs$numericdf[10,3],3)
  m$`0.975-CI.Pl-Pu`<-list(round(rs$numericdf[10,4],3))
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))

@@

}
#----------------------------------
#calling the above function on 4 multivariable datasets
m1<-multivar_tab_summary_fn(r=RES_aphid_count,rs=stat_aphid_count)
m2<-multivar_tab_summary_fn(r=RES_aphid_ff,rs=stat_aphid_ff)
m3<-multivar_tab_summary_fn(r=RES_plankton_north_sea,rs=stat_plankton_north_sea)
m4<-multivar_tab_summary_fn(r=RES_methane,rs=stat_methane)
tab_multivar_summary<-cbind(m1,m2,m3,m4)
colnames(tab_multivar_summary)<-c("Green-spruce aphid_count","Leaf-plum curling aphid_firstflight","C. furca_count","Methane-flux")
saveRDS(tab_multivar_summary,"./Results/tab_multivar_summary.RDS")
```

>>>>

@@

  m<-matrix(NA,1,18)
  colnames(m)<-c("num.pairs","num.non.indep","num.non_N",
                 "Avg.N_minus_bestfit.AICw","Avg.N_minus_bestfit.AIC","num.good.fit",
                 "LT_0.025_CI","LT_0.975_CI","UT_0.025_CI","UT_0.975_CI",
                 "percent.LT_minus_UT_gt0",
                 "Corl_0.025_CI","Corl_0.975_CI","Coru_0.025_CI","Coru_0.975_CI",
                 "avg.Corl_minus_Coru","Corl_minus_Coru_0.025_CI","Corl_minus_Coru_0.975_CI")
  m<-as.data.frame(m)

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$num.non.indep<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)

  bcop<-r$info_ord_copcode[,,1] # matrix with best fit copula name
  bcop[bcop==Inf]<-NaN # replacing Independent pairs with NaN
  m$num.non_N<-sum(bcop!=1,na.rm = T)

@@

  pcvm<-r$gfc_p_CvM
  pcvm[pcvm==Inf]<-NaN
  pks<-r$gfc_p_KS
  pks[pks==Inf]<-NaN
  temp<-which((pcvm>0.01) & (pks>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$LT_0.025_CI<-round(CI_LT[1],3)
  m$LT_0.975_CI<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$UT_0.025_CI<-round(CI_UT[1],3)
  m$UT_0.975_CI<-round(CI_UT[2],3)
  m$percent.LT_minus_UT_gt0<-round((sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)/((d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)))*100,2)
  m$Corl_0.025_CI<-round(rs$numericdf[3,3],3)
  m$Corl_0.975_CI<-round(rs$numericdf[3,4],3)
  m$Coru_0.025_CI<-round(rs$numericdf[4,3],3)
  m$Coru_0.975_CI<-round(rs$numericdf[4,4],3)
  m$avg.Corl_minus_Coru<-round(rs$numericdf[9,2],3)
  m$Corl_minus_Coru_0.025_CI<-round(rs$numericdf[9,3],3)
  m$Corl_minus_Coru_0.975_CI<-list(round(rs$numericdf[9,4],3))
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))

@@

}
#----------------------------------
#calling the above function on 4 multivariable datasets
m1<-multivar_tab_summary_fn(r=RES_aphid_count,rs=stat_aphid_count)
m2<-multivar_tab_summary_fn(r=RES_aphid_ff,rs=stat_aphid_ff)
m3<-multivar_tab_summary_fn(r=RES_plankton_north_sea,rs=stat_plankton_north_sea)
m4<-multivar_tab_summary_fn(r=RES_methane,rs=stat_methane)
tab_multivar_summary<-cbind(m1,m2,m3,m4)
colnames(tab_multivar_summary)<-c("Green_spruce_aphid_count","Leaf_plum_curling_aphid_firstflight","C_furca_count","Methane_flux")
saveRDS(tab_multivar_summary,"./Results/tab_multivar_summary.RDS")
```
